Numerical Analysis \\ Assignment 7

### 2017-11-09 Graduate - Introduction to Analysis I/Assignment 6/assignment.tex

\problem{3}{Problem 35, Section 4.4, Page 90}
\solution{Proof}{
Denote $f_n(x) = f(x, a_n) $, in which $\{a_n\}$ is any series which converges to 0. Then from the condition we know $f_n(x) $ converges pointwise to $f(x)$, and $|f_n(x)| \le g(x)$. Then using Lebesgue Dominated Convergence Theorem, since $g$ is integrable on $[0, 1]$, we have
$$
\lim_{n\to\infty} \int_{0}^{1}f_n(x)dx = \int_{0}^{1} f(x)dx.
$$
It shows that 
$$
\limsup_{y\to 0}\int_{0}^{1}f(x, y)dx = \liminf_{y\to 0}\int_{0}^{1}f(x, y)dx = \int_{0}^{1}f(x)dx, 
$$
whic means 
$$
\lim_{y\to 0}\int_{0}^{1}f(x, y) dx = \int_{0}^{1}f(x)dx.
$$
For the continuity of $h$, we need to show that $\forall y_0 \in [0, 1]$, $\forall \epsilon > 0$, $\exists \delta > 0$, when $|y-y_0| <\delta $, we have $h(y)-h(y_0) = |\int_{0}^{1}f(x, y)dx-\int_{0}^{1}f(x, y_0)|dx < \epsilon$. Since $f(x, y)$ is continuous in $y$ for each $x$, then for each fixed $x$, $\exists \delta_1$, when $|y-y_0| <\delta_1 $, $|f(x, y)-f(x, y_0)| < \epsilon$. Then 
$$
|h(y)-h(y_0)| = \left|\int_{0}^{1} f(x, y)dx - \int_{0}^{1} f(x, y_0)dx\right| \le \int_{0}^{1} |f(x, y)-f(x, y_0)|dx < \epsilon.
$$
We know the continuity of $h$ since we can pick $\delta = \delta_1 $.
}

@@

\problem{5}{Problem 38, Section 4.5, Page 91}
\solution{(i)}{
$$
\lim_{n\to\infty}\int_{0}^{n} fdx = \lim_{n\to\infty}\sum_{m = 1}^{n}\frac{(-1)^m}{m} = -\ln2,
$$
But
$$
\int_{1}^{\infty}f^+ = \sum_{m=1}^{\infty}\frac{1}{2m} = \infty,
$$
So $f$ is not integrable.
}
\solution{(ii)}{
$$
\lim_{n\to\infty}\int_{1}^{n}f = \int_{1}^{\infty}\frac{\sin x}{x}dx,
$$
with Dirichlet's Criterion, we know this integral converges. But
$$
\int_{1}^{\infty}|f| \ge \int_{1}^{\infty}\frac{1}{2x}dx - \int_{1}^{\infty}\frac{\cos 2x}{x}dx,
$$
and the second term converges with Dirichlet's Criterion, but the first term $\to\infty$, we know this integral diverges to $\infty$. Thus $f$ is not integrable.

>>>>

\problem{3}{Problem 35, Section 4.4, Page 90}
\solution{Proof}{
Denote $f_n(x) = f(x, a_n) $, in which $\{a_n\}$ is any series which converges to 0. Then from the condition we know $f_n(x) $ converges pointwise to $f(x)$, and $|f_n(x)| \le g(x)$. Then using Lebesgue Dominated Convergence Theorem, since $g$ is integrable on $[0, 1]$, we have
$$
\lim_{n\to\infty} \int_{0}^{1}f_n(x)dx = \int_{0}^{1} f(x)dx.
$$
It shows that 
$$
\limsup_{y\to 0}\int_{0}^{1}f(x, y)dx = \liminf_{y\to 0}\int_{0}^{1}f(x, y)dx = \int_{0}^{1}f(x)dx, 
$$
whic means 
$$
\lim_{y\to 0}\int_{0}^{1}f(x, y) dx = \int_{0}^{1}f(x)dx.
$$
For the continuity of $h$, we need to show that $\forall y_0 \in [0, 1]$, $\forall \epsilon > 0$, $\exists \delta > 0$, when $|y-y_0| <\delta $, we have $h(y)-h(y_0) = |\int_{0}^{1}f(x, y)dx-\int_{0}^{1}f(x, y_0)dx| < \epsilon$. Since $f(x, y)$ is continuous in $y$ for each $x$ in a closed set, then $f(x, y)$ is uniformly bounded, then for each $x$, $\exists \delta_1$, when $|y-y_0| <\delta_1 $, $|f(x, y)-f(x, y_0)| < \epsilon$. Then 
$$
|h(y)-h(y_0)| = \left|\int_{0}^{1} f(x, y)dx - \int_{0}^{1} f(x, y_0)dx\right| \le \int_{0}^{1} |f(x, y)-f(x, y_0)|dx < \epsilon.
$$
We know the continuity of $h$ since we can pick $\delta = \delta_1 $.
}

@@

\problem{5}{Problem 38, Section 4.5, Page 91}
\solution{(i)}{
$$
\lim_{n\to\infty}\int_{1}^{n} fdx = \lim_{n\to\infty}\sum_{m = 1}^{n}\frac{(-1)^m}{m} = -\ln2,
$$
But
$$
\int_{1}^{\infty}f^+ = \sum_{m=1}^{\infty}\frac{1}{2m} = \infty,
$$
So $f$ is not integrable.
}
\solution{(ii)}{
$$
\lim_{n\to\infty}\int_{1}^{n}f = \int_{1}^{\infty}\frac{\sin x}{x}dx,
$$
with Dirichlet's Criterion, we know this integral converges. But
$$
\int_{1}^{\infty}|f| \ge \int_{1}^{\infty}\frac{1}{2x}dx - \int_{1}^{\infty}\frac{\cos 2x}{x}dx,
$$
and the second term converges with Dirichlet's Criterion, but the first term $\to\infty$, we know this integral diverges to $\infty$. Thus $f$ is not integrable.

### 2017-11-09 Graduate - Numerical Analysis/Assignment 7/assignment.tex
update

>>>>

\problem{4}{For $n = 1, \cdots, 10$, generate the Newton divided difference polynomials that interpolates $\cos(x) ~\text{for}~ x \in [0, 2\pi]$, at n equally spaced points. Create an error table.}
\solution{Solution}{
The code and result (the graph of error and table of Max error) is listed below.
}
\lstinputlisting[language = MATLAB]{newton_poly.m}
\lstinputlisting[language = MATLAB]{prob4.m}

\begin{figure}[!htb]
\centering
\includegraphics[width = 0.5\textwidth]{prob4.eps}
\caption{Error of interpolation with different order}
\end{figure}
\begin{lstlisting}[language = MATLAB]
>> prob4
   1.0e+03 *

    0.0020
    0.0020
    0.0040
    0.0045
    0.0520
    0.1047
    0.2818
    0.9745
    1.0237
    7.0735
\end{lstlisting}

\problem{5}{For $n = 1,\cdots, 5$, construct Hermite interpolant that interpolates $\cos(x) ~\text{for}~ x \in [0, 2\pi]$, at $n$ equally spaced points. Create an error table.
}
\solution{Solution}{
The code and result is as below. It seems Hermite intepolation is more stable then Newton intepolation.
}
\lstinputlisting[language = MATLAB]{Hermite_poly.m}
\lstinputlisting[language = MATLAB]{prob5.m}
\begin{figure}[!htb]
\centering
\includegraphics[width = 0.5\textwidth]{prob5.eps}
\caption{Error of Hermite interpolation with different order}
\end{figure}
\begin{lstlisting}[language = MATLAB]
>> prob5
    2.0000
    4.0801
    0.8723
    0.0900
    0.0056
\end{lstlisting}
